Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-16 WSSSPE3/report/wg_appendix_industry_interaction.tex
change in appendix title to match main section
beefing up 5.3 appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Industry Interaction Working Group Discussion}
\label{sec:appendix_industry_interaction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Our initial broad question was, "What makes for successful transitions of scientific software from academia to industry?"

There are a number of potential funding transitions that may occur:  
%
\begin{itemize}

@@

@@

\subsection{Description of Opportunity, Challenges, and Obstacles}

@@

\subsection{Plan for Future Organization}

\subsection{What Else is Needed?}

\subsection{Key Milestones and Responsible Parties}

\subsection{Description of Funding Needed}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Transition Pathways to Sustainable Software: Industry \& Academic Collaboration Working Group Discussion}
\label{sec:appendix_industry_interaction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Our initial broad question was, "What makes for successful transitions of scientific software from academia to industry?" There are a number of potential funding transitions that may occur:  
%
\begin{itemize}

@@

\item The project could gain attention from a industry use case who would potentially make in-kind
contributions by having paid staff contribute to the software.

@@

\subsection{Description of Opportunity, Challenges, and Obstacles}
The opportunity is to create a catalog of success/failure for current and future software projects to be prepared for transitions and achieve sustainability of the software.

The obstacle is more superficial, in finding a champion to gather such information. It will be a challenge to keep this information and surveys updated. With changing rapidly changing industry landscapes, an obsolete survey could be of less or no use.

@@

\subsection{Plan for Future Organization}
No concrete plans were made at this point. If community can rally behind, some momentum could be built. If you are interested post at \url{https://github.com/WSSSPE/meetings/issues/46}

\subsection{What Else is Needed?}
Nothing at the moment.

\subsection{Key Milestones and Responsible Parties}
A key portion of this effort will require focused surveys of projects which have succeeded and failed in transition. Both these categories will yield good learning on what works and what does not work. The group has identified what needs to be studied further, but has not identified responsible parties to conduct them.

Community could help in gathering data by means of Interviews; Historical documents / documentation and Surveys

An example data collection will be: 
\begin{itemize}
\item Origin: Where did project start? 
\item People involved: How many people in original project were involved in transition/collaboration? 
\item Specs on software
\item Language
\item Size
\item Hardness (age)
\item Lead-up to Transition: How long was project in development before it began transition?
\item Motivation for Transition: Why was transition initiated? By whom? 
\end{itemize}

\subsection{Description of Funding Needed}
Concrete funding needs were not discussed in this working group but a general impression was a seed funding will motivate members of this group or others in community to launch a survey effort.

### 2016-01-16 WSSSPE3/report/wg_main_industry_interaction.tex
beefing up 5.3 appendix

Most scientific software is produced as a part of grant-funded research projects
sponsored by federal governments. If we are interested in the sustainability of
scientific software, then we need to understand what exactly happens when that
sponsorship ends. More than likely, the project and its resulting software will
need to undergo some kind of transition in funding and consequently management.

At WSSSPE3 our group was interested in better understanding successful pathways
for scientific software to ``transition'' from government-funded research
projects to industry sponsorship. (This may be an initially awkward
phrase---some software projects will begin their life being sponsored by
industry, or result in collaboration between industry and academia. In such
cases, there is still a need to understand how IP and how maintenance of the
software is sustained over time.)

@@

Although sustainability transitions are often studied under the broad umbrella of ``technology
transfer,'' we believe there are likely to be a number of different ways in which
a pathway from initial production to long-term maintenance and secure funding is
achieved. In short, industry sponsorship is an important aspect of sustaining
scientific software, but our current understanding of these transitions focuses
narrowly on commercial successes or failures of those collaborations.

@@

\subsubsection{Landing Page}

In lieu of a landing page, the Transitions Pathways
group requests an email be sent to Nic Weber\footnote{email: 
\href{mailto:nmweber@uw.edu}{nmweber@uw.edu}} to find out more
about the group's efforts and how to participate.

>>>>

Most scientific software is produced as a part of grant-funded research projects typically 
sponsored by federal governments. If we are interested in the sustainability of
scientific software, then we need to understand what exactly happens when that
sponsorship ends. More than likely, the project and its resulting software will
need to undergo some kind of transition in funding and consequently governance.

At WSSSPE3 our group was interested in better understanding successful pathways
for scientific software to ``transition'' from grant-funded research
projects to industry sponsorship. (This may be an initially awkward
phrase---some software projects will begin their life being sponsored by
industry, or result in collaboration between industry and academia. In such
cases, there is still a need to understand how IP and how maintenance of the
software is sustained over time.)

@@

Although sustainability transitions are often studied under the broad umbrella of ``technology
transfer,'' we believe there are likely to be a number of different ways in which
a pathway from initial production to long-term maintenance and secure funding is
achieved. In short, industry sponsorship and/or direct participation is an important aspect of sustaining
scientific software, but our current understanding of these transitions focuses
narrowly on commercial successes or failures of those collaborations.

@@

\subsubsection{Landing Page}
Transitions Pathways discussions can be posted at \url{https://github.com/WSSSPE/meetings/issues/46} or an email be sent to Nic Weber\footnote{email: \href{mailto:nmweber@uw.edu}{nmweber@uw.edu}} to find out more about the group's efforts and how to participate.
